An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-12-18 article.tex
fixed table

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia (SWA), Australia's national wine industry sustainability program. SWA aims to support grape growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \small
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{Number of Classes} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & KGs of Nitrogen & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. For this case study, related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source. Further details about these variables, their classes and their frequency is available in the Appendix.
\par
The variable Region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Compared to revenue, the predictive performance of XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most iomportant predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, Region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Operating Costs using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most important variables in predicting Region using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}
\section{Discussion}

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting Year using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:year_sankey}
 \end{figure}

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most important variables in predicting revenue using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit}
 \end{figure}

>>>>

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia (SWA), Australia's national wine industry sustainability program. SWA aims to support grape growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing (see Appendix for more information).}\label{tab:summary}
 \small
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}lccc@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Number of Classes} & \textbf{No. Records} \\ \midrule
  Water Used & Mega Litres &  & 5846 \\
  Diesel & Litres &  & 5585 \\
  Biodiesel & Litres &  & 25 \\
  LPG & Litres &  & 958 \\
  Herbicide Spray & No. Times per year &  & 2026 \\
  Year & Class & 10 & 6049 \\
  Disease & Class & 2 & 6049 \\
  Region & Class & 58 & 6049 \\
  Solar & Kilowatt Hours &  & 622 \\
  Irrigation Type & Class & 20 & 6049 \\
  Petrol & Litres &  & 4309 \\
  Slashing & No. Times per year &  & 2290 \\
  Yield & Tonnes &  & 5935 \\
  Irrigation Energy & Class & 16 & 6049 \\
  Area Harvested & Hectares &  & 6049 \\
  Electricity & Kilowatt Hours &  & 1014 \\
  Insecticide Spray & No. Times per year &  & 1092 \\
  Fertiliser & KGs of Nitrogen &  & 795 \\
  Fungicide Spray & Times per year &  & 2260 \\
  Cover Crop & Class & 32 & 6049 \\
  Water Type/Source & Class & 39 & 6049 \\
  Grape Revenue & AUD &  & 853 \\
  Operating Costs & AUD &  & 853 \\ \bottomrule
  \end{tabular}
  \end{table}
\normalsize
The data originally contained only two multiclass variables: year and region. For this case study, related binary variables, such as the use of river water and the use of dam water, were combined to create multiclass variables such as water source/type. Further details about these variables, their classes and their frequency is available in the Appendix.
\par
The variable Region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

Compared to revenue, the predictive performance of XGBoost model for operating cost was slightly better, with an $R^2$ of 0.80 (with a standard deviation of 0.10). Similar to revenue, the most iomportant predictors of operating cost were fuel, water, area and yield (see figure \ref{fig:operating_costs_sankey}). A surprising difference was the change in relative importance of activities involving tractor passes where the use of fungicide was more important for operational costs, compared to revenue, where slashing was more important (see Figure \ref{fig:region_sankey}). The variables that feed into these decisions are also very different with diesel having the highest relative importance to slashing, and area having the greatest relative importance to the need for fungicide.
\par
Again, Region played a determining factor overall, contributing to 334 nodes within the ensemble making it the most important variable when considering all regions together. It was surprising that electricity, slashing and spraying passes were not more prominent in operating costs due to the intrinsic nature as an agricultural expense.
\par
% . Again the surrogate model did not perform well achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) but showed similarly to revenue an importance placed on fungicide spraying and size (see figure \ref{fig:operating_tree}).
\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{operating_costs.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative  important variables in predicting Operating Costs using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:operating_costs_sankey}
 \end{figure}

@@

\begin{figure}[htb]
  \resizebox{\textwidth}{!}{
  \includegraphics{region.png}}
  \caption{The left-hand side, A,  depicts the 10 most relative important variables in predicting Region using XGBoost as a measure of node occurrence, using a Sankey diagram. The number at the end of each band in the diagram is that variable's importance. The right-hand side, B, depicts the importance of the 10 variables in Sankey diagram relative to one another.}\label{fig:region_sankey}
 \end{figure}
\section{Discussion}

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{year.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting Year using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:year_sankey}
 \end{figure}

@@

 \begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{profit.png}}
  \caption{The left-hand side depicts the 10 most relative important variables in predicting revenue using XGBoost as a measure of node occurrence, using a Sankey diagram. The right-hand side depicts the interrelated importance of the ten predictor variables using a chord diagram.}\label{fig:profit}
 \end{figure}
